---
title: "Titanic Data Analysis"
author: "Ahmed Ashraf Mohamed"
output: 
  hrbrthemes::ipsum_pdf:
    toc: yes
    number_sections: yes
    includes:
      in_header: preamble.tex
    highlight: pygments
  html_document:
    toc: yes
    df_print: paged
    
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,  dev = "cairo_pdf")
```

# Preliminary Look at the data

We need first to define the data we have.   

| Variable | Definition                                    | Key                                            |
|:-------------------|:-------------------------|:-------------------------|
| survival | Survival                                      | 0 = No, 1 = yes                                |
| pclass   | ticket class                                  | 1 = 1st, 2 = 2nd, 3 = 3rd                      |
| sex      | sex                                           |                                                |
| age      | Age in year                                   |                                                |
| sibsp    | Number of siblings/spouses aboard the titanic |                                                |
| parch    | Number of parents/children aboard the Titanic |                                                |
| ticket   | ticket number(unique)                         |                                                |
| fare     | Passenger fare                                |                                                |
| cabin    | Cabin number                                  |                                                |
| embarked | port of embarkation                           | C = Cherbourg, Q = Queenstown, S = Southampton |

```{r echo=TRUE, results='hide',message=FALSE}
# Loading Packages
library(tidyverse)
library(viridis)
library(ggplot2)
library(ggcorrplot)
library(ggthemes)
library(hrbrthemes)
library(e1071)
library(mice)
library(statsr)


# Loading Data
train <- read_csv("data/train.csv")
test <- read_csv("data/test.csv")
```

# Exploration Of The Data

## Summary of Data

```{r}
summary(train)
```

## Plotting The Data

### Correlation Matrix (numerical analysis)
We are going to use correlation matrix of the numerical data to assess the correlation, which might gives a better idea of which feature might be important
```{r}
train %>%
  filter(!is.na(Age)) %>%
  select(Survived, Pclass,Age,SibSp,Parch,Fare) %>%
  cor() %>%
  ggcorrplot(lab = T,
             ggtheme =theme_ipsum_rc(grid = F),
             title="Correlation Matrix",hc.order=T,
             colors =rev(viridis(3,alpha=0.7)),
             digits = 2)
```

The fare features seems to be the most correlated feature to survival of the passengers, but it doesn't negate the importance of the other features in the data. Which means that we will start by comparing the each that we consider to be important against survival feature

### Class of Passenger
```{r}
train %>%
  select(Pclass,Survived) %>%
  ggplot(aes(as_factor(Pclass),fill=as_factor(Survived))) + 
  geom_bar(position = "fill") +
  scale_y_continuous(labels=scales::percent) +
  theme_ipsum_rc() + 
  labs(x = "Classes",y = "Survival Rate")+
  scale_fill_discrete(name = "Survived", labels = c("Didn't Survive","Survived")) 
```

### Siblings and Spouses
```{r}
train %>%
  select(SibSp,Survived) %>%
  ggplot(aes(as_factor(SibSp),fill=as_factor(Survived))) +
  geom_bar(position = "fill") + 
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Siblings and Spouses",y = "Survival Rate")+
  scale_fill_discrete(name = "Survived", labels = c("Didn't Survive","Survived"))+
  theme_ipsum()
```

### Number of children/parents
```{r}
train %>%
  select(Parch,Survived) %>%
  ggplot(aes(as_factor(Parch),fill=as_factor(Survived))) + 
  geom_bar(position = "fill") +
  scale_y_continuous(label = scales::percent)+
  labs(x = "Number of parents/children",y = "Survival Rate")+
  scale_fill_discrete(name = "Survived", labels = c("Didn't Survive","Survived")) +
  theme_ipsum_rc()
```

```{r}
head(train)
train %>%
  group_by(Sex) %>%
  summarise(Age_mean = mean(Age,na.rm=TRUE),
            age_sd = sd(Age,na.rm=T),
            surival_mean = mean(Survived,na.rm =T),
            surival_sd = sd(Survived,na.rm = T))

```
# Description of the data
## Categorical Features
## Numerical Features