---
title: "Titanic Data Analysis"
author: "Ahmed Ashraf Mohamed"
output:
  pdf_document: 
    toc: yes
    number_sections: yes
    includes:
      in_header: preamble.tex
    highlight: pygments
  html_document:
    toc: yes
    df_print: paged
---

# Preliminary Look at the data

The

| Variable | Definition                                    | Key                                            |
|:-------------------|:-------------------------|:-------------------------|
| survival | Survival                                      | 0 = No, 1 = yes                                |
| pclass   | ticket class                                  | 1 = 1st, 2 = 2nd, 3 = 3rd                      |
| sex      | sex                                           |                                                |
| age      | Age in year                                   |                                                |
| sibsp    | Number of siblings/spouses aboard the titanic |                                                |
| parch    | Number of parents/children aboard the Titanic |                                                |
| ticket   | ticket number(unique)                         |                                                |
| fare     | Passenger fare                                |                                                |
| cabin    | Cabin number                                  |                                                |
| embarked | port of embarkation                           | C = Cherbourg, Q = Queenstown, S = Southampton |

```{r}
library(tidyverse)
library(ggthemes)
train <- read_csv(file = "data/train.csv")

train <- train %>%
  mutate(Sex = as_factor(Sex),Embarked = as_factor(Embarked))

head(train)
tail(train)
```

# Summary of the Data

```{r}
summary(train)
```

## Grouped by Sex

```{r}
head(train)
train %>%
  group_by(Sex) %>%
  summarise(Age_mean = mean(Age,na.rm=TRUE),
            age_sd = sd(Age,na.rm=T),
            surival_mean = mean(Survived,na.rm =T),
            surival_sd = sd(Survived,na.rm = T))



```
# Description of the data
## Categorical Features
## Numerical Features