---
title: "Assignment-1"
author: "Ahmed Ashraf Mohamed ID:2103134"
output: pdf_document
---


# Importing the libraries and the data

```{r libraries, include=FALSE}
library(statsr)
library(dplyr)
library(ggplot2)
```
Importing the data and printing it.
```{r}
data("ames")
print(ames)
```
# Exercise 1

```{r}
price_sample <- ames %>% sample_n(size = 50)
price_sample %>%
summarise(mu = mean(price),
          pop_med = median(price),
          sigma = sd(price), pop_iqr = IQR(price),
          pop_min = min(price),pop_max = max(price),
          pop_q1 = quantile(area, 0.25),
          pop_q3 = quantile(area, 0.75))

```

# Exercise 2

```{r}
sample_means50 <- ames %>%
rep_sample_n(size = 50, reps = 5000, replace = TRUE) %>%
summarise(x_bar = mean(price))

ggplot(data = sample_means50, aes(x = x_bar)) + geom_histogram(binwidth = 30)

```
Based on this plot, it seem that the distribution is a normal distribution.
Eyeing this the means seems around 180,000 mark, to make sure we are going to print the mean of our sample.
```{r}
print(paste("Mean : ",mean(sample_means50$x_bar)))
```
# Exercise 3

```{r}
sample_means150 <- ames %>%
rep_sample_n(size = 150, reps = 5000, replace = TRUE) %>%
summarise(x_bar = mean(price))

ggplot(data = sample_means150, aes(x = x_bar)) + geom_histogram(binwidth = 30)

```
Looking at this plot and comparing it to the previous plot, it seems clear that the mean is just a bit higher than 180,000, also noting that both plots are normal distributions.
```{r}
print(paste("Mean:",mean(sample_means150$x_bar)))
```
# Exercise 4

```{r}
price_sample15 <- ames %>% sample_n(size = 15)
print(as_tibble(price_sample15$price))
print(mean(price_sample15$price))

```

# Exercise 5

```{r}
sample_means15 <-ames %>%
  rep_sample_n(size = 15,reps = 2000,replace = TRUE) %>%
  summarise(x_bar = mean(price))

ggplot(data = sample_means15, aes(x = x_bar)) + geom_histogram(binwidth = 30)
print(mean(sample_means15$x_bar))
```

## Population Summary 

```{r summary}
ames %>%
summarise(mu = mean(price),
          pop_med = median(price),
          sigma = sd(price), pop_iqr = IQR(price),
          pop_min = min(price),pop_max = max(price),
          pop_q1 = quantile(area, 0.25),
          pop_q3 = quantile(area, 0.75))
```
# Exercise 6
```{r}
sample_means150 <-ames %>%
  rep_sample_n(size = 150,reps = 2000,replace = TRUE) %>%
  summarise(x_bar = mean(price))

ggplot(data = sample_means150, aes(x = x_bar)) + geom_histogram(binwidth = 30)
print(mean(sample_means150$x_bar))
```